\section{Results}

\subsection{Selection of events}

In the Netherlands, several festivals and parties are organized on a large scale that attract a lot of visitors. Because a very small amount of numbers are known about drug use in the Netherlands at certain events and holidays, it is hard to say at which events drug use is more popular than others. [bron] For this reason, the research focused on news articles showing high levels of drug use at various events. In order to conduct a proper analysis within the time frame, five events were chosen.  

\subsubsection{Unpopularity of drug use}

A small survey of drug use at various events revealed that not all major events in the Netherlands involve high levels of drug use. A remarkable aspect is that at De Zwarte Cross, the largest festival in the Netherlands with 220 thousand visitors, hard drugs are not popular among the audience. De Zwarte Cross is originally a cross race that lasts 3 days combined with music and performances by various bands. At De Zwarte Cross a lot of alcohol is consumed in particular. [bron] In addition, it appears that Carnival, a multi-day festival celebrated in the south of the Netherlands, also mainly consumes a lot of alcohol and has much less interest in hard drugs. [bron] 

It can be explained that drugs do not have a major presence at these large events because drugs are mainly used during dance festivals where mainly techno and house music is listened. According to [bron], 70\% of dance festival visitors use drugs. Both at De Zwarte Cross and during Carnival, this style of music is not played very frequently and this could be a reason for the unpopularity of drug use during those events.

However, the Amsterdam Dance Event (ADE) appears to be a popular event for drug use. [bron] During this multi-day dance festival that consists of multiple parties spread across multiple locations in Amsterdam, a lot of techno and house music is played. This would support the explanation of drug use and certain parties and festivals. 
Another festival where drugs appear to be widely used is Lowlands. [bron] This festival lasts one weekend in the beginning of August where various artists around the world perform at this festival. 

Besides these big festivals, many parties and smaller festivals take place during certain holidays in the Netherlands. For example, Koningsdag, one day every year where the Dutch celebrate the king's birthday, is a real festivity. According to several articles, many people also use drugs during this day. [bron]  Not only during Koningsdag many people appear to use drugs also during the GayPride and New Year's Eve. The Gay Pride is a multi-day celebration with different events organized in several cities in the Netherlands. During Gay Pride, many Dutch people celebrate freedom of sexuality. This party has a gay cultural character and is known to involve a lot and also many different types of drugs. [bron]

Overall, the five events identified based on this news-article survey where drugs are commonly used are;

\begin{enumerate}
  \item Amsterdam Dance Event (ADE)
  \item Lowlands
  \item Kingsday
  \item Pride Amsterdam
  \item New Years Eve
\end{enumerate}

\subsubsection{Established time period}

So for the research in this report, those five events are used as events with a high level of drug use of the visitors. Furthermore, the time period of each event is set to 1 week in which the event takes place. In this way the preparations for the event on the popularity of drugs are also included in the research. To carry out the research as automatically as possible, it is difficult to set a different time period for different events, such as ADE, which itself lasts a week, in which the preparations will also be included. Therefore it is decided to consider all events as one week events and Future Work will describe how the research could be adapted for longer events. 

\subsection{Selection of drugs}

For this research in which drugs and specific events in the Netherlands are analyzed, it is important to determine the specific drugs under investigation. Because of the limited timeframe for this research and the variety of drugs in the Netherlands nowadays, it is chosen to select three types of drugs. If the outcomes of the three drugs contain interesting results or will serve other potential purposes, the research could also be conducted for multiple drugs and displayed in the final dashboard. More on this will be discussed in Future Work.

The three drugs that are used in this study and are visualized in the resulting visualization are based on the statistics from the National Drug Monitor. The National Drug Monitor (NDM) is a Dutch organization that collects and compiles all data on drug use, the drug market and drug-related crime of all ages in the population through different monitors. The purpose of this institution is to provide a clear representation of all the data monitored in the Netherlands related to drugs. 

One of those representations is given in Figure X. This figure shows for each drug how much it has been used among the Dutch population in recent years. This figure shows that the most commonly used drug, with a significant difference, is cannabis. In addition, it can be seen that XTC is a commonly used drug in the Netherlands and cocaine is in third place. As can be seen in the figure, the line representing the drug Nitrous oxide (Lachgas) is interrupted because no results are known about this drug before that time. For that reason this drug is not included in the research at all. The other drugs visible in the figure that are not so often used are Heroine, Amphetamine, Paddo’s, LSD, and GHB.

To investigate the popularity of drugs it is more interesting for the police to look at hard drugs that are illegal to possess and use than at the tolerated drugs for which the police cannot intervene. For this reason, although the soft drug cannabis is the most commonly used drug in the Netherlands, it is not investigated further.

As concluded above, the two most commonly used hard drugs in the Netherlands are XTC and cocaine. Because these are the most used hard drugs they are expected to be the most popular drugs in the Netherlands which can be interesting for the research. 

Besides that, it is chosen to include a less used hard drug in the research. This decision is made to investigate whether less frequently used hard drugs are also less frequently searched on Google and appear in news articles than the commonly used hard drugs and whether those drugs are related to specific events (and how) or not. According to figure X from the National Drug Monitor, GHB is a rarely used drug in the Netherlands and therefore GHB is examined as the third drug. along with cocaine and XTC in this report. 

So for this research, three drug types that are specified as cocaine, XTC and GHB are investigated, because it provides sufficient results for the Police Academy and fits within the time span for this research. 

\subsection{Proportion test results}

To answer the main research question and the two subquestions ‘How could we identify drug popularity at events?’ and ‘What are the differences between the specific events and drugs?’, proportion tests have been performed on the google trends, twitter and NOS data for the three types of drugs. Thus, the mean proportion of peaks for all weeks from 2014 until 2022 has been compared to the proportion of peaks for specific drug events. For each test the null hypothesis (H0) stated: the proportion of peaks observed in drug related event weeks is not significantly larger than the proportion of peaks in regular weeks. The alternative hypothesis (H1) for each test stated: drug related event weeks have a significantly higher proportion of peaks compared to the regular weeks in the year.

\subsubsection{XTC}

The results show that for the drug XTC and the Google Trends data, King’s Day (p < .001), New Year’s Eve (p < .001) and Amsterdam Dance Event (p = .009) have rejected H0. However, Lowlands (p = .700) and the Amsterdam Gay Pride Event (p = .183) did not show a significant difference. Therefore, three out of five events have a strong significant difference with the mean proportion Google trends data for the drug XTC.

However, statistics for the Twitter data on the drug XTC show that for King’s Day (p = .977), New Year’s Eve (p = .461), Amsterdam Dance Event (p = .461), Lowlands (p = .211) and the Amsterdam Gay Pride (p = .760) H0 has not been rejected. Thus, Twitter data did not show any significant difference between the mean proportion of all weeks and the proportion of the weeks of all events.

Furthermore, the results show that the NOS articles also did not have a significant difference of peaks proportions. Since, King’s Day (p = .264), , New Year’s Eve (p = .887), Amsterdam Dance Event (p = .544), Lowlands (p = .544) and the Amsterdam Gay Pride (p = .887) all did not reject H0. Thus, the drug XTC proved to only have a strong significant relationship with the Google Trends data and the events King’s day, New Year’s Eve and Amsterdam Dance Event.

\subsubsection{Cocaine}

For the drug Cocaine the results do not show any significant outcomes for the Google Trends data. As King’s Day (p = .067), New Year’s Eve (p = .435), Amsterdam Dance Event (p = .205), Lowlands (p = .205) and the Amsterdam Gay Pride (p = .731) do all show p-values higher than 0.05. However, the p-value of King’s Day (p = .067) is only slightly higher than the critical p-value. 

	Moreover, the results show that for Cocaine and the Twitter data, King’s Day (p = .200), New Year’s Eve (p = .745) and Amsterdam Gay Pride Event (p = .973) have not rejected H0.  Amsterdam Dance Event (p = .055) and Lowlands (p = .055) show p-values quite low. Nevertheless, the p-values of ADE and Lowlands are not high enough to reject H0. Therefore, Cocaine does also not show a significant difference between the mean proportion of the Twitter data and the proportion of the events. 

	Lastly, statistics do not show that Cocaine and the NOS articles have a difference in the proportion of peaks with the proportion of peaks of any event. For King’s Day (p = .561), , New Year’s Eve (p = .373), Amsterdam Dance Event (p = .676), Lowlands (p = .373) and the Amsterdam Gay Pride (p = .952) all did not reject H0. Thus, Cocaine does not show any significant higher proportion of peaks between the different data sources and the events.

\subsubsection{GHB}

The test results for the drug GHB and the Google trends data show that for the event of King’s Day (p = .011) it rejects H0. New Year’s Eve (p = .205), Amsterdam Dance Event (p = .067), Lowlands (p = .970) and Amsterdam Gay Pride (p = .067) do not show any significant results. However, the p-value of both Amsterdam Dance Event and Amsterdam Gay Pride is only slightly above the critical value. Therefore, for the drug GHB, Google Trends only show a significant difference in peaks for King’s Day.

Additionally, the statistics demonstrate that for GHB, Twitter does not have a significant difference in peaks with the events. Since, King’s Day (p = .472), New Year’s Eve (p = .979), Amsterdam Dance Event (p = .219), Lowlands (p = .472) and the Amsterdam Gay Pride (p = .219) did all not prove to be significant.

Finally, the NOS articles also do not show any significant results for the drug GHB. King’s Day (p = .516), New Year’s Eve (p = .516), Amsterdam Dance Event (p = 1.00), Lowlands (p = .516) and the Amsterdam Gay Pride (p = .216) all do not reject H0. Thus, out of all data sources, the drug GHB only shows a significantly higher proportion of peaks for Google Trends during King’s Day . 

In conclusion, the test results show that the subquestion ‘How could we identify drug popularity at events?’ can be answered by stating that Google Trends, with a score of four, has the highest number of significant proportions of peaks for the events in total. In contrast with Twitter and the NOS articles where none of the events demonstrated to have a significant proportion of peaks for all types of drugs tested. 

Concerning the last subquestion ‘What are the differences between the specific events and drugs?’, there is a difference found between the specific events. The statistics of the proportion tests demonstrated that the events Lowlands and the Amsterdam Gay Pride never reject H0 for any type of drug tested, while King’s Day, New Year’s Eve and ADE did reject H0 for the drug XTC. Additionally, King’s Day proved to have a significantly higher proportion of peaks for the drug GHB as well.